Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-22 paper/icml_drau/framework.tex

Many reinforcement learning environments are not intrinsically
time-discrete, but discretizations of an underlying continuous-time
environment. For instance, many simulated control environments, such as
the Mujoco environments~\cite{ddpg} or OpenAI Gym classic control
environments~\cite{gym}, are discretization of continuous-time control
problems.  In simulated environments, the time discretization is fixed by
the simulator, and is often used to approximate an underlying
differential equation.  \TODO{(For example) $->$ In this case}, the timestep may correspond to the
number of frames generated by second.  In real world environments,
sensors and actuators have a fixed time precision: cameras can only
capture a fixed amount of frames per second, and physical limitations
prevent actuators from responding instantaneously. The quality of these
components thus imposes a lower bound on the discretization timestep. As
the timestep $\deltat$ is not an intrinsic parameter of the
environment, but a constraint imposed by computational ressources, we
would expect that decreasing $\deltat$ could only improve the performance
of RL agents \TODO{We would remove: (though it might make optimization
harder) It is not in the spririt of what is said here. NDY keep it.
Anyone with a bit of experience in traditional optim would scream and say exactly
that, if it was not included.}.  RL algorithms should, at least, be resilient to a change of
$\deltat$, and should remain viable when $\deltat \rightarrow 0$.
Besides, designing a time discretization invariant algorithm could
alleviate tedious hyperparameterization by providing better defaults for
time-horizon-related parameters.

>>>>

Many reinforcement learning environments are not intrinsically
time-discrete, but discretizations of an underlying continuous-time
environment. For instance, many simulated control environments, such as
the Mujoco environments~\cite{ddpg} or OpenAI Gym classic control
environments~\cite{gym}, are discretization of continuous-time control
problems.  In simulated environments, the time discretization is fixed by
the simulator, and is often used to approximate an underlying
differential equation.  In this case, the timestep may correspond to the
number of frames generated by second.  In real world environments,
sensors and actuators have a fixed time precision: cameras can only
capture a fixed amount of frames per second, and physical limitations
prevent actuators from responding instantaneously. The quality of these
components thus imposes a lower bound on the discretization timestep. As
the timestep $\deltat$ is not an intrinsic parameter of the
environment, but a constraint imposed by computational ressources, we
would expect that decreasing $\deltat$ could only improve the performance
of RL agents (though it might make optimization
harder).  RL algorithms should, at least, be resilient to a change of
$\deltat$, and should remain viable when $\deltat \rightarrow 0$.
Besides, designing a time discretization invariant algorithm could
alleviate tedious hyperparameterization by providing better defaults for
time-horizon-related parameters.
